Sex, education, and mental health: Analyzing American census data through statistical methods, 2018 to 2021

### 2024-10-24 paper/paper.qmd
Update paper.qmd to correct Figure 5's caption
Update paper.qmd to change 'leverage' to 'use'

@fig-age The histogram demonstrates the overview of the age data distribution, depicting the high and low frequencies. The highest concentration of respondents is above the age of 60. Our dataset has a relatively low representation of the younger population.

@@

We leverage the logistic regression model to identify the association between suffering from psychological distress with sex and education. We set our model following the @tellingstories guidelines with the rstanarm package [@rstanarm_goodrich, @rstanarm_brilleman] in R [@citer].

>>>>

@fig-age demonstrates the overview of the age data distribution, depicting the high and low frequencies. The highest concentration of respondents is above the age of 60. Our dataset has a relatively low representation of the younger population.

@@

We use a logistic regression model to identify the association between suffering from psychological distress with sex and education. We set our model following the @tellingstories guidelines with the rstanarm package [@rstanarm_goodrich, @rstanarm_brilleman] in R [@citer].
